---
title: "Chapter of course"
output: html_document
---


```{r, include = FALSE}
# leanbuild::set_knitr_image_path()
```

## Learning Objectives

This chapter will cover:  

- {You can use https://www.bu.edu/cme/forms/RSS_forms/tips_for_writing_objectives.pdf to define some learning objectives here}
- {Another learning objective}

## Libraries

For this chapter, we'll need the following packages attached: 

```{r}
library(here)
library(ggplot2)
library(magrittr)
```

# Topic of Section

Text Text

## Subtopic

Text Text 

### Code examples

```{r}
output_dir <- "code_output"
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}
```

```{r}
iris %>%
  ggplot(aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point() +
  theme_bw()
```

```{r}
ggsave(file.path(output_dir, "test_ggplot2.png"))
```

### Image example

```{r, fig.align='center', echo = FALSE, fig.alt= "Major point!! example image"}
leanbuild::include_slide("https://docs.google.com/presentation/d/1YmwKdIy9BeQ3EShgZhvtb3MgR8P6iDX4DfFD65W_gdQ/edit#slide=id.gcc4fbee202_0_141")
```


### Video examples


```{r, fig.align="center", fig.alt = "video", echo=FALSE, out.width="100%"}
knitr::include_url("https://www.youtube.com/embed/yiZQaE0q9BY")
```

```{r, fig.align="center", fig.alt = "video", echo=FALSE, out.width="100%"}
knitr::include_url("https://www.youtube.com/embed/VOCYL-FNbr0")
```

### Embedded files examples


```{r, fig.align="center", echo=FALSE}
knitr::include_url("https://www.messiah.edu/download/downloads/id/921/Microaggressions_in_the_Classroom.pdf", height = "800px")
```

```{r, fig.align="center", echo=FALSE}
knitr::include_url("https://widgets.figshare.com/articles/5427418/embed?show_title=1", height = "800px")
```

Example of including a website:
```{r, fig.align="center", echo=FALSE}
knitr::include_url("https://yihui.org", height = "800px")
```

Example of including an html file hosted on GitHub:

```{r, fig.align="center", echo=FALSE}
knitr::include_url("https://carriewright11.github.io/stringr_RLadies/index.html", height = "800px")
```


### Citation examples

We can put citations at the end of a sentence like this [@bookdown2016]. 
Or multiple citations [@bookdown2016, @rmarkdown2018]. 

but they need a ; separator [@bookdown2016; @rmarkdown2018]. 

but they need a ; separator [ \[@bookdown2016\](#bookdown2016); \[@rmarkdown2018\](#rmarkdown2018)]. 

In text, we can put citations like this @bookdown2016. 


Here's a silly example which may mess up references.

```{r}
library(oro.nifti)
img <- oro.nifti::nifti()
img@.Data
```

## Print out session info

```{r}
devtools::session_info()
```
